# pre-class


Make sure you commit this often with meaningful messages. 


### Question 1:

Using a loop, print the integers from 1 to 50. 
```{r}
printing <- function () {
  for (i in 1:50) {
  print(i)
  }
}
```

### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
500500
```{r}
x = 0
for (i in 0:1000) {
  x = x + i
}
```

B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
250500
```{r}
y = 0
for (i in seq(0, 1000, by = 2)) {
  y = y + i
}
```

C. Now, repeat A and B WITHOUT using a loop.
```{r}
a = c(0:1000)
sum(a)

b = seq(0,1000, by=2)
sum(b)
```

### Question 3:

Here is a dataframe of survey data containing 5 questions :

```{r, eval=FALSE}
survey <- data.frame(
                     "participant" = c(1, 2, 3, 4, 5, 6),
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2)
                     )
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.
```{r}
# version where participant number is left untouched
survey.clean = data.frame()
for (i in 1:nrow(survey)) {
  for (j in 1:ncol(survey)) {
    if (j == 1) {
      survey.clean[i,j] = survey[i,j]
    } else if (survey[i,j] < 1 || survey[i,j] >5) {
      survey.clean[i,j] = NA
    } else {
      survey.clean[i,j] = survey[i,j]
    }
  }
}

# version where anything not between 1 and 5 is changed
survey.clean2 = data.frame()
for (i in 1:nrow(survey)) {
  for (j in 1:ncol(survey)) {
    if (survey[i,j] < 1 || survey[i,j] >5) {
      survey.clean2[i,j] = NA
    } else {
      survey.clean2[i,j] = survey[i,j]
    }
  }
}
```

B. Now, again using a loop, add a new column to the dataframe called “invalid.answers” that indicates, for each participant, how many bad answers they gave.
```{r}
survey2 = survey.clean2
survey2$invalid.answers=""
for (i in 1:nrow(survey2)) {
  for (j in 1:ncol(survey2)) {
    count = 0
    if (is.na(survey2[i,j])) {
      count = count + 1
      survey2[7:j] = count
    }
  }
}
```
