Use dplyr functions to address the following questions:

```{r}
library(dplyr)
library(gapminder)
gapminder
```

How many unique countries are represented per continent?
33 in Asia, 52 in Africa, 25 in Americas, and 2 in Oceania.
```{r}
data <- gapminder

data %>%
  group_by(continent) %>%
  summarize(unique=length(unique(country)))
```

Which European nation had the lowest GDP per capita in 1997?
Albania
```{r}
low_gdp <- data %>%
  filter(continent == "Europe", year == 1997) %>%
  arrange(gdpPercap)

low_gdp[1,]
```

According to the data available, what was the average life expectancy across each continent in the 1980s?
Africa 52.5, Americas 67.2, Asia 63.7, Europe 73.2, Oceania 74.8
``` {r}
data %>% 
  group_by(continent) %>%
  filter(year >= 1980 & year < 1990) %>%
  summarize(life=mean(lifeExp))
```

What 5 countries have the highest total GDP over all years combined?
Kuwait, Switzerland, Norway, US, Canada

```{r}
data %>%
  group_by(country) %>%
  summarize(total_gdp=sum(gdpPercap)) %>%
  arrange(desc(total_gdp)) %>%
  filter(row_number() %in% 1:5)
```

What countries and years had life expectancies of at least 80 years? N.b. only output the columns of interest: country, life expectancy and year (in that order).
```{r}
data %>%
  filter(lifeExp > 80) %>%
  select(country, lifeExp, year)
```

What 10 countries have the strongest correlation (in either direction) between life expectancy and per capita GDP?
Note: The 10 strongest correlations were all positive, but if there were really strong negative correlations, would we take the absolute value of all the correlations and rank them that way?
```{r}
corr <- data %>%
  group_by(country) %>%
  summarize(correlation=cor(lifeExp,gdpPercap)) %>%
  arrange(desc(correlation))

filter(corr,row_number()%in% 1:10)
```

Which combinations of continent (besides Asia) and year have the highest average population across all countries? N.b. your output should include all results sorted by highest average population. With what you already know, this one may stump you. See this Q&A for how to ungroup before arrangeing. This also behaves differently in more recent versions of dplyr.
```{r}
high_avg <- data %>%
  filter(continent != "Asia") %>%
  group_by(continent, year) %>%
  summarize(avg_pop = mean(pop)) %>%
  arrange(desc(avg_pop))
# confused because I think I did it without ungrouping? But I'm also not arranging by anything I used to group by.
```

Which three countries have had the most consistent population estimates (i.e. lowest standard deviation) across the years of available data?
Sao Tome & Principe, Iceland, Montenegro
```{r}
sd_pop <- data %>%
  group_by(country) %>%
  summarize(stand_dev=sd(pop)) %>%
  arrange(stand_dev)

sd_pop[1:3,]
```

Subset gm to only include observations from 1992 and store the results as gm1992. What kind of object is
this?

``` {r}
gm1992 <- subset(data, year == 1992)
class(gm1992)
# tbl, tbl.df, & data frame?
```

Which observations indicate that the population of a country has decreased from the previous year and the life expectancy has increased from the previous year? See the vignette on window functions.

```{r}
data %>%
  group_by(country, year) %>%
  filter(lag(pop) > pop, lifeExp > lag(lifeExp))

```





