# pre-class

Make sure you commit this often with meaningful messages. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
# returns string depending on length of prefix, then compares the two for equality
compare_strings <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}

# returns last element in x, given it is more than legnth 1
returns_last <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}

# repeat vector y for the length of x
repeat_vect <- function(x, y) {
  rep(y, length.out = length(x))
}
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
rnorm()'s arguments are n, mean, and sd, while mvrnorm()'s are n, mu, and sigma. 


3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 
```{r}
new_mtcars = lapply(mtcars, function(x) {sd(x)/mean(x)})
```

4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
```{r}
calc_sd = function(df) {vapply(df, sd, numeric(1))}
```
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)
```{r}
calc_sd_mixed = function(df) {vapply((df[vapply(df, class, character(1)) == "numeric"]), sd, numeric(1))}
```
    


