---
output:
  pdf_document: default
  html_document: default
---
# pre-class

Make sure you commit this often with meaningful messages. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
# returns string depending on length of prefix, then compares the two for equality
compare_strings <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}

# removes last element in x, given it is more than legnth 1
removes_last <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}

# repeat vector y for the length of x
repeat_vect <- function(x, y) {
  rep(y, length.out = length(x))
}
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
rnorm() draws from a normal distribution, & mvrnorm() draws from a multivariate normal distribution. rnorm()'s arguments are n, mean, and sd, while mvrnorm()'s are n, mu, and sigma. 
To make the arguments more consistent with what they actually represent, mvrnorm()'s mu argument should indicate that mu is a vector argument with values each representing the means for the variables they represent (eg vect_of_means).  The sigma argument should indicate that it is a matrix representing the covariance matrix (eg covar_mtrx).
In terms of making an estimate more consistent to the true population value, you could increase sample sizes (the n parameters). 


3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 
```{r}
new_mtcars = lapply(mtcars, function(x) {sd(x)/mean(x)})
```

4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
```{r}
calc_sd = function(df) {vapply(df, sd, numeric(1))}
```
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)
```{r}
calc_sd_mixed = function(df) {vapply((df[vapply(df, class, character(1)) == "numeric"]), sd, numeric(1))}
```